Association between trauma severity models and opportunities for improvement:

### 2022-12-15 manuscript.Rmd
.

```{r, echo=FALSE, out.width = "400px"}
knitr::include_graphics("images/ofi.png") ## ofi_diagram.R; save_png(ofi_diagram(), "ofi") to update
```

@@

```{r} 
  table.one ## will be improved later
```

>>>>

```{r, echo=FALSE, out.width = "400px"}
knitr::include_graphics("images/ofi.png") ## ofi_diagram.R; save_png(ofi_diagram(), "ofi") to update
## titles for plots will be added in word
```

@@

```{r} 
  table.one
```
